Towards Verifying the Bitcoin-S Library

### 2020-07-15 paper-short/main.tex
add short paper

\documentclass[runningheads]{llncs}

% to have bookmarks in pdf
% remove for final version
\usepackage[open,openlevel=5]{bookmark}
\setcounter{tocdepth}{5}

\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%

@@

\usepackage{hyperref}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}

%\usepackage{courier}
\usepackage{listings, color}
\hypersetup{
  colorlinks   = true,
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = blue
}

% latin modern, no more bitmap fonts in pdf
\usepackage{lmodern}
%\usepackage{newtxtext}
%\usepackage{newtxmath}
\usepackage[zerostyle=b,scaled=.88]{newtxtt}

% nicer bold
\renewcommand{\bfdefault}{b}%

% make paragraph headings bold instead of italics
\renewcommand{\paragraph}{\textbf}%

@@

\newcommand{\todo}[1]{{\par \color{red}#1}}

@@

\title{Towards Verifying the Bitcoin-S Library}

\author{Ramon Boss \and Kai Brünnler \and Anna Doukmak}

\authorrunning{R. Boss et al.}
\institute{Bern University of Applied Sciences, CH-2501 Biel, Switzerland
\email{ramon.boss@outlook.com, kai.bruennler@bfh.ch,\\anna.doukmak@gmail.com}}

@@

\begin{abstract}
  We try to verify properties of the bitcoin-s library, a Scala
  implementation of parts of the Bitcoin protocol. We use the
  Stainless verifier which supports programs in a fragment of Scala
  called \emph{Pure Scala}. Since bitcoin-s is not written in this
  fragment, we extract the relevant code from it and perform a series
  of equivalent transformations until we arrive at code that we
  successfully verify. In that process we find and fix two bugs in
  bitcoin-s.

\keywords{Bitcoin \and Scala \and bitcoin-s \and Stainless.}
\end{abstract}

@@

\bibliographystyle{splncs04}

@@

\clearpage
\appendix

>>>>

\documentclass[hyphens, a4paper,USenglish,cleveref, autoref, thm-restate]{oasics-v2019}
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"

@@

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Towards Verifying the Bitcoin-S Library} %TODO Please add

%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

\author{Ramon Boss}{Bern University of Applied Sciences, Switzerland}{ramon.boss@outlook.com}{}{}
\author{Kai Brünnler}{Bern University of Applied Sciences, Switzerland}{kai.bruennler@bfh.ch}{}{}
\author{Anna Doukmak}{Bern University of Applied Sciences, Switzerland}{anna.doukmak@gmail.com}{}{}

\authorrunning{R. Boss and K. Brünnler and A. Doukmak} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Ramon Boss and Kai Brünnler and Anna Doukmak} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003790.10002990</concept_id>
<concept_desc>Theory of computation~Logic and verification</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Logic and verification}

\keywords{Bitcoin, Scala, Bitcoin-S, Stainless} %TODO mandatory; please add comma-separated list of keywords

%\category{} %optional, e.g. invited paper

\relatedversion{A full version of the paper is available at
  \url{https://github.com/kaibr/bitcoin-s-verification/blob/master/paper/paper.pdf}.}

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

%\funding{(Optional) general funding statement
% \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

%\acknowledgements{I want to thank \dots}%optional

\nolinenumbers %uncomment to disable line numbering

%\hideOASIcs  %uncomment to remove references to OASIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{listings, color}

@@

@@

@@

\begin{abstract}
  We try to verify properties of the Bitcoin-S library, a Scala
  implementation of parts of the Bitcoin protocol. We use the
  Stainless verifier which supports programs in a fragment of Scala
  called \emph{Pure Scala}. Since Bitcoin-S is not written in this
  fragment, we extract the relevant code from it and perform a series
  of equivalent transformations until we arrive at code that we
  successfully verify. In that process we find and fix two bugs in
  Bitcoin-S.
\end{abstract}

@@

\appendix

@@
